spatial_figures

### 2024-07-16 spatial_figs.Rmd
reminders
updating sept13 edit html
updating

# update the HRUs
hru_new <- vect('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')
plot(hru_new)

hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp') %>%

mapview(hru_new)

@@

# Figure 1b-e -- NEED TO REDO WITH WHOLE CATCHMENT DATA

@@

# difference

@@

#grid first
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/grid_all")

@@

#statn next
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/statn_all")

>>>>

# update the HRUs
hru_new <- vect('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')
plot(hru_new)

hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')

mapview(hru_new) + mapview(hru_test)
mapview(hru_test)

@@

# Figure 1b-e -- NEED TO REDO WITH WHOLE CATCHMENT DATA and UPDATED MODELS

@@

# difference - UPDATE file sources!!

@@

#grid first
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/grid")

@@

#statn next
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/statn")
